---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---
## Loading and preprocessing the data
```{r}
df = read.csv("./activity.csv", stringsAsFactors = FALSE)
#df$date = strptime(df$date, format = "%Y-%m-%d")
```

## What is mean total number of steps taken per day?
###Histogram of total numbers of steps per day
```{r}
new_df = df[which( !is.na(df$steps) ), ]
# sum over steps in the same day:
histo = aggregate(new_df$steps, by = list(new_df$date), FUN = sum) 
# rename column just to be more clear:
names(histo) = c('Date', 'tot_steps')
# plot the histogram:
hist(histo$tot_steps, col = 'red', xlab = 'Total number of steps per day', main = 'Histogram')
```

###Mean and median of the total number of steps per day:
```{r}
mean(histo$tot_steps)
median(histo$tot_steps)
```

## What is the average daily activity pattern?
###Time series plot:
```{r}
data = aggregate(new_df$steps, by = list(new_df$interval), FUN = mean)
names(data) = c('interval', 'tot_steps')
plot(data$interval, data$tot_steps, type = 'l', xlab = 'interval', ylab = 'tot_steps', main = 'Average over all days of total number of steps vs interval')
```

###Interval with the maximun number of steps:
```{r}
data[ which( data$tot_steps == max(data$tot_steps) ), 'interval']
```

## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
